On The Benefits of Magnitude Estimation Relevance Assessments for Information Retrieval Evaluation

### 2016-09-14 0_abstract.tex
Added a note that I don't like the abstract. Added a reference to Aroyo & Welty and some text in 2.3, marked in response.tex
Remember to write crowdsourcing as a single word.

\begin{abstract}

Magnitude estimation is a psychophysical scaling technique for the
measurement of sensation, where observers assign numbers to stimuli in
response to their perceived intensity.
We investigate the use of magnitude estimation for judging the
relevance of documents for information retrieval
evaluation, carrying out a large-scale user study across 18 TREC topics
and collecting
over 50,000 magnitude estimation judgments using crowd sourcing.
Our analysis shows that, on average, magnitude estimation judgments are
rank-aligned with ordinal judgments made by expert relevance assessors.
%An advantage of magnitude estimation is that users can chose their own
%scale for judgments, allowing deeper investigations of user perceptions
%than when categorical scales are used.

>>>>

\begin{abstract}
\sm{I don't like this abstract...}

Magnitude estimation is a psychophysical scaling technique for the
measurement of sensation, where observers assign numbers to stimuli in
response to their perceived intensity.
We investigate the use of magnitude estimation for judging the
relevance of documents for information retrieval
evaluation, carrying out a large-scale user study across 18 TREC topics
and collecting
over 50,000 magnitude estimation judgments using crowdsourcing.
Our analysis shows that, on average, magnitude estimation judgments are
rank-aligned with ordinal judgments made by expert relevance assessors.
%An advantage of magnitude estimation is that users can chose their own
%scale for judgments, allowing deeper investigations of user perceptions
%than when categorical scales are used.

### 2016-09-14 2_bg.tex
Added a note that I don't like the abstract. Added a reference to Aroyo & Welty and some text in 2.3, marked in response.tex
Remember to write crowdsourcing as a single word.

>>>>

\sm{It is important to remark that disagreement might not mean low quality. 
  As claimed for example by \citet{aroyo2015truth}, disagreement might
  depend on the false assumption of a ``unique truth'', it might carry
  useful information that can be exploited, and attempts to eliminate
  disagreement, for example by detailed instructions, might not
  improve quality and simply lead to information loss.}
